\vspace{-15mm}\fontsize{24pt}{10pt}\selectfont\textbf{A Radial Time Projection Chamber for $\alpha$ detection in CLAS at JLab}

### 2017-10-18 eg6-letters/NIM/EG6_RTPC_NIM.tex
more updated to the NIM paper

%\begin{keywords}
%Time projection chamber, gas electron multipliers, alpha particles, DVCS, 
%Nuclear physics
%\end{keywords}

@@

To calibrate the gains, we compared the experimental ADCs to the energy deposited 
for each pad individually in GEANT4 by similar simulated tracks (using the 
same elastic events as for the drift 
paths calibration). This requires a very good GEANT4 simulation 
including drift paths, but also the spread of the charge along the path
before reaching the pad, so that the simulated hits match the experimental 
ones. Moreover, the simulation has to match the DAQ features 
that can lead to cutting out hits. After setting the simulation properly, we 
compared simulation to experiment on an event by event basis as shown in 
Figure~\ref{fig:EVENT_adc_tdc}. The gain for each pad was calculated as the 
ratio of the measured ADCs to the simulated deposited energy.  Then, these 
gains were refined using correction factors obtained from a sample of good 
tracks. For each track, we calculate the corrected energy deposit on a pad and 
compared it to the average
deposit recorded by the other pads. This last step was implemented to 
avoid any bias from this simulation based calibration method.
Final results are shown in Figure~\ref{fig:dedx_p_exp_2nd}, where energy loss 
of particles is plotted against momentum over charge ratio. One can clearly see 
the band for $^4$He in its expected position.

\begin{figure}[tb!]
   \centering
\includegraphics[scale=0.42]{Event_ADC_Graph_8799283.pdf}
\caption{Simulated (upper) and experimental (lower) ADC and T distributions 
of a track. The colors indicate the pads, same color in top and bottom indicate 
that they are the same pad.}
\label{fig:EVENT_adc_tdc}
\end{figure}

\begin{figure*}[tb]
\centering
\includegraphics[scale=0.73]{f_dedx_p_exp_2nd.pdf}
\caption{$\small{\frac{dE}{dX}}$ vs. $p/q$ distributions for the left (on the 
   left) and for the right (on the right) half of the RTPC after gain 
   calibration. The lines are theoretical expectations from the Bethe-Bloch 
   formula for $^4$He 
   (red), $^3$He (black), $^3$H (blue), $^2$H (pink) and protons (gray).}
\label{fig:dedx_p_exp_2nd}
\end{figure*}

>>>>

\begin{keywords}
Time projection chamber, gas electron multipliers, alpha particles, DVCS, 
Nuclear physics
\end{keywords}

@@

To calibrate the gains, we compared the experimental ADCs to the energy 
deposited for each pad individually in GEANT4 by similar simulated tracks 
(using the same elastic events as for the drift paths calibration). This 
requires a very good GEANT4 simulation including drift paths and the spread of 
the charge along the path before reaching the pad, so that the simulated hits 
match the experimental ones. Moreover, the simulation has to match the DAQ 
features that can lead to cutting out some hits. After setting the simulation 
properly, we compared simulation to experiment on an event by event basis as 
shown in Figure~\ref{fig:EVENT_adc_tdc}. The gain for each pad was calculated 
as the ratio of the measured ADCs to the simulated deposited energy. Then, This 
set of the gains was applied to the experimental data. We noticed that some 
pads record lower ADCs than expected. For this reason, we wanted to make sure 
that the recorded ADCs by a given pad are similar to the ADCs recorded by other 
pads in the same track. At this step, we compared the mean ADCs of each
pad to the mean ADCs of the whole track. This ratio is collected for each pad 
from a sample of elastic events and a gain correction factor is extracted and 
applied to the first extracted gain ratio giving a final gain for each readout 
pad. Final results are shown in Figure~\ref{fig:dedx_p_exp_2nd}, where energy 
loss of particles is plotted against momentum over charge ratio. One can 
clearly see the band for $^4$He in its expected position.

\begin{figure}[tb]
   \centering
\includegraphics[scale=0.42]{Event_ADC_Graph_8799283.pdf}
\caption{Simulated (upper) and experimental (lower) ADC and T distributions 
of a track. The colors indicate the pads, same color in top and bottom indicate 
that they are the same pad.}
\label{fig:EVENT_adc_tdc}
\end{figure}

\begin{figure*}[tp]
\centering
\includegraphics[scale=0.73]{f_dedx_p_exp_2nd.pdf}
\caption{$\small{\frac{dE}{dX}}$ vs. $p/q$ distributions for the left (on the 
   left) and for the right (on the right) half of the RTPC after gain 
   calibration. The lines are theoretical expectations from the Bethe-Bloch 
   formula for $^4$He 
   (red), $^3$He (black), $^3$H (blue), $^2$H (pink) and protons (gray).}
\label{fig:dedx_p_exp_2nd}
\end{figure*}

### 2017-10-18 eg6-letters/NIM/review-1/review-1.tex
more updated to the NIM paper

\item Figure 6: why are $T_{min}$ and $T_{max}$ not at the drift gap 
   extremities?\\
   \textcolor{blue}{This is a schematic to illustrate the definitions of 
   $T_{min}$ and $T_{max}$ for a chain hits. The figure can be modified if 
needed.}

@@

\item line 306: "in one bin" should be explained better. I understood it is the 
   subdivision in bins of the z coordinate, but it was not so obvious at the 
   first reading\\
\textcolor{blue}{Cleared}

\item Has the stability of the drift path been counter checked with simulations 
   varying the field according to the cathode radius variation? How much is the 
   field variation if the radius have some mm of uncertainty?\\
\textcolor{blue}{We did not study this case.}

        /paragraph 4.3
\item The gain calibration is very quick. I would like more details, e.g. 
   "setting the simulation properly" intends only GEANT4 or also MAGBOLTZ or 
   GARFIELD? Were they used to simulate the drift and avalanche formation of 
   the electrons? And the diffusion from the gas? Was a specific code written 
   to simulate the electronics?\\
\textcolor{blue}{ }

\item line 330: "correction factors" are mentioned. On what? Why haven't only 
   good tracks been used for calibration? Lack of statistics?\\
\textcolor{blue}{ }

\item When it says that the pad charge is "compared" to the neighboring ones, 
   what happens next? Is it the noise reduction step described later? If so, 
   please write it. \\
\textcolor{blue}{ }

\item Figure 11: I don't understand it. How many tracks does the histo contain? 
   If the single pad has 128 channels, how many channels does the single bin 
   contain? Moreover, is the dE calculated on pad by pad basis? In that case, 
   why don't you put just one point in the histo for each pad? What is the mean 
   number of channels or pads fired by one track? Sorry for the list of 
   questions, but I could not understand the figure.\\
\textcolor{blue}{ }

\item Figure 12 - please, put if after figure 11. Moreover, please change dEdx 
   to dE/dx on y axis. Why are the left and right pictures so different? 
   Talking about the deuteron band which is present only in the left figure and 
   the smear on the top part of the right picture. \\
\textcolor{blue}{ }

@@

\item < dE/dx > is computed here as corrected Etot divided total track length. 
   Usually the mean dE/dx is computed with the truncated mean of the specific 
   energy losses of each hit. Isn't it possible to compute it like this here? 
   dx for each hit can be (maybe) computed from the difference in the hit 
   times. Sum $dE_{i}$/Sum $dx_{i}$ is not equal to Sum ($dE_{i}/dx_{i}$).\\
\textcolor{blue}{ }

>>>>

\item Figure 6: why are $T_{min}$ and $T_{max}$ not at the drift gap 
   extremities?\\
   \textcolor{blue}{This is a schematic to illustrate the definitions of 
   $T_{min}$ and $T_{max}$ in a chain of hits. The figure can be modified if 
needed.}

@@

\item line 306: "in one bin" should be explained better. I understood it is the 
   subdivision in bins of the z coordinate, but it was not so obvious at the 
   first reading\\
\textcolor{blue}{The text is cleared}

\item Has the stability of the drift path been counter checked with simulations 
   varying the field according to the cathode radius variation? How much is the 
   field variation if the radius have some mm of uncertainty?\\
\textcolor{blue}{We did not study this case. }

        /paragraph 4.3
\item The gain calibration is very quick. I would like more details, e.g. 
   "setting the simulation properly" intends only GEANT4 or also MAGBOLTZ or 
   GARFIELD? Were they used to simulate the drift and avalanche formation of 
   the electrons? And the diffusion from the gas? Was a specific code written 
   to simulate the electronics?\\
\textcolor{blue}{Only GEANT4 simulation was used in performing the gain 
   calibration, where the drift paths are updated in the simulation. The 
   electrons avalanche formation and the gas diffusion are performed though 
GEANT4. We did not implement a detailed description to simulate the 
electronics, but we did apply similar conditions to match the real DAQ, such as 
the rejection of the signals from bad pads and conditions to ensure that each 
pad must have at least 3 consecutive time bins, with ADC values above the 
threshold, 35 ADCs, in order to be recorded. The text is cleared with more 
details. }

\item line 330: "correction factors" are mentioned. On what? Why haven't only 
   good tracks been used for calibration? Lack of statistics?\\
\textcolor{blue}{Correction factor on the extracted gain for each pad. We used 
the elastic $^4$He tracks as we could calculate the recoil $^4$He kinematics 
from the scattered electron in CLAS to avoid any discrepancy from the RTPC.}

\item When it says that the pad charge is "compared" to the neighboring ones, 
   what happens next? Is it the noise reduction step described later? If so, 
   please write it. \\
\textcolor{blue}{The gain extraction is following this order: \\
- pass 1: the gain of each pad is defined as the ratio between the mean 
recorded experimental ADCs to the mean simulated ADCs in the same track. Then 
for each pad, the gain ratios were collected from all the identified elastic 
tracks and these gains were fitted by a Landau function to give a
  first pass gain for each pad as the most probable value of the fit.\\
 - pass2: to make sure that the recorded ADCs by a given pad are similar to the 
 recorded ADCs by other pads in the same track, we refined this calibration 
 after the extracted gains were applied to the experimental data. At this step, 
 we compared the mean ADCs of each pad to the mean ADCs of the whole track. 
 This ratio is collected from all the elastic events and a gain correction 
 factor is extracted and applied giving a final gain for each pad.
  }

\item Figure 11: I don't understand it. How many tracks does the histo contain? 
   If the single pad has 128 channels, how many channels does the single bin 
   contain? Moreover, is the dE calculated on pad by pad basis? In that case, 
   why don't you put just one point in the histo for each pad? What is the mean 
   number of channels or pads fired by one track? Sorry for the list of 
   questions, but I could not understand the figure.\\
   \textcolor{blue}{- It is for only one track (written in the caption).
   - We dont understand your second question. A pad is a channel. Do you mean 
how many pads are fired for a single track? Figure \ref{npd_track} shows the 
number of active pads as a function of the momentum for the collected elastic 
$^4$He tracks.\\
- dE is calculated from the ADCs of the individual pads that read out hits 
  corresponding to the same track. One needed to know the individual step size 
  very precisely to put dEdx from the individual pads, which is not available.  
  - Last question is addressed by figure \ref{npd_track}. The mean value is 
    around 10 pads. }

\begin{figure}[h!]
   \centering
   \includegraphics[scale=0.45]{npd_p_elastic.png}
   \caption{The number of active pads versus the measured momentum of the 
   elastic $^4$He tracks. } \label{fig:npd_track}
\end{figure}

\item Figure 12 - please, put it after figure 11. Moreover, please change dEdx 
   to dE/dx on y axis. Why are the left and right pictures so different?  
   Talking about the deuteron band which is present only in the left figure and 
   the smear on the top part of the right picture. \\
\textcolor{red}{- The figures layout will be updated.\\}

\textcolor{blue}{- The y-axis label on figure 12 is updated.\\}
\textcolor{blue}{- Regarding the lower peak in the left module of the RTPC, 
   these events pass all the elastic requirements but for some reasons they 
   have lower ADC values.  They represent around 7\% of all the elastic events.  
   After extended studies, the nature of these particles is not identified yet.  
   We note that this is a global phenomenon in the left module as 94\% of the 
   left module's pads are involved in both some low and high dEdx events. For 
   the calibration procedures, the events with low dEdx were excluded as we do 
not fully understand their nature.}

@@

\item < dE/dx > is computed here as corrected Etot divided total track length. 
   Usually the mean dE/dx is computed with the truncated mean of the specific 
   energy losses of each hit. Isn't it possible to compute it like this here? 
   dx for each hit can be (maybe) computed from the difference in the hit 
   times. Sum $dE_{i}$/Sum $dx_{i}$ is not equal to Sum ($dE_{i}/dx_{i}$).\\
\textcolor{blue}{Maybe this would improve our calculations for dEdx by few 
percent, but a precise hits ordering is needed to compute dEdx as you suggest, 
which is not available in our setting.}
